The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation history.

### 2022-09-01 src/tex/ms.tex
comments verwerkt

% Title
% \title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate  }
% \title{ A flexible expression for the metallicity-dependent cosmic star formation rate: }
\title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation.}

@@

%%%%%%%%%%%%%%%
\author[0000-0001-5484-4987]{L.~A.~C.~van~Son}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
60 Garden St., Cambridge, MA 02138, USA}
\affiliation{Anton Pannekoek Institute of Astronomy and GRAPPA, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
\author[0000-0001-5484-4987]{et. al}
% %%%%%%%%%%%%%%%
% \author[0000-0001-9336-2825]{S. E. de Mink}
% \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
% \affiliation{Anton Pannekoek Institute of Astronomy and GRAPPA, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
% \affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
% %%%%%%%%%%%%%%%
% \author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
% \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
% %%%%%%%%%%%%%%%
% \author[0000-0002-8901-6994]{L. Hernquist}
% \affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
% 60 Garden St., Cambridge, MA 02138, USA}
% %%%%%%%%%%%%%%%
% \author[0000-0003-3308-2420]{R. Pakmor}
% \affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract with filler text
\begin{abstract}
New observational facilities are probing astrophysical transients such as stellar explosions and gravitational wave (GW) sources at ever increasing redshifts. To interpret these observation we need to compare them to predictions from stellar population models. These models, require the metallicity-dependent star formation rate density (\SFRDzZ) as an input. Large uncertainties remain in the shape and evolution of this function, and understanding its behaviour is essential to explain simulation results. 
% Large uncertainties remain in the value and shape of the \SFRDzZ, especially at the low metallicities that are crucial to the formation of GW events.
% Understanding the behaviour of the adopted metallicity distribution with which stars form is essential to explain simulation results. 
% Various approaches to approximate \SFRDzZ exist, ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
In this work, we propose a simple analytical function for \SFRDzZ. 
% The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
Variations of this function can be easily interpreted, because the parameters link to its shape in an intuitive way. %Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
We fit our analytical function to the star-forming gas of the cosmological TNG100 simulations and find that it is able to capture the main behaviour well. 
%
As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH). Our main findings are I) the location of features is remarkably robust against variations in the metallicity-dependent star formation rate and II) the low mass end is least affected by these variations. This is promising as it increases our chances to constrain the physics that governs the formation of these objects.
We further find that III) the skewness, mean, and width of the metallicity distribution at low redshift affect the overall rate, while IV) the redshift evolution of the width and the mean of the metallicity distribution affects the slope at the high-mass end of the distribution. 
% IV) the shape of the overall star-formation rate has a small impact on the local mass distribution.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction \label{sec: intro}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe. Exotic transient phenomena, including (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events appear to be especially sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe \citep[e.g.,][]{Langer+2007,Fruchter+2006,LIGO2016_implications}.
Gravitational astronomy in particular has seen explosive growth in the number of detections in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}. In order to correctly model and interpret these observations, it is fundamental to know the rate of star formation at different metallicities throughout cosmic history, i.e. the metallicity-dependent star formation rate density  \citep[\SFRDzZ, see also the recent review by][]{chruslinska2022_review}. Throughout this work little $z$ refers to the redshift and $Z$ the metallicity of star formation.

It is difficult to observationally constrain the shape of \SFRDzZ, see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats. Even at low redshifts, the low metallicity part of the distribution is poorly constrained \citep{Chruslinska+2021}.
Nonetheless, several methods exist to estimate the metallicity dependent star-formation rate.

The first method combines a galaxy mass-metallicity relation, MZ-relation and a galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}. However, the applied methods to infer galaxy properties and subsequently scaling relations such as the MZ-relation differ greatly, which makes it difficult to interpret these results in a consistent way \citep[e.g.,][]{KewleyEllison2008,MaiolinoMannucci2019,Cresci+2019}. Moreover, observations are generally incomplete at high redshifts and low galaxy luminosity \citep[e.g.,][]{Chruslinska+2021}.

% \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
One can also directly extract the metallicity density fraction from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}. However, these simulations currently lack the resolution to resolve the lowest mass galaxies, and their variations in \SFRDzZ span a smaller range than those observed in observationally-based models \citep{Pakmor+2022}.

Alternatively, one can combine analytical models for the observed star formation rate, \SFRDz, like those from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with an assumed function for the shape of the shape of the metallicity density distribution, such as was was done in e.g., \cite{LangerNorman, Neijssel+2019}.

%Arguments: cosmological simulations work at high z,  but are they real? observations 
In this work we follow the latter approach and propose a flexible analytical model for the \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available. 
In contrast to earlier work, we adopt a skewed-lognormal distribution of metallicities that can capture the asymmetry in the low and high metallicity tails. %\citep{LangerNorman, Neijssel+2019}

The purpose of this proposed form is twofold.  
First of all, the form we propose allows for an intuitive interpretation of the free parameters. This allows us to get better insight of the impact of changes in these parameters on the inferred ranges of astrophysical transients (as we demonstrate in Section \ref{sec: mass dists} using GW predictions as an example). By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties can be systematically explored.
%
Secondly, both the large complications in observational constraints, and the many uncertainties in cosmological simulations call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available. % which is the motivation for this work. 
In particular, the advent of observations with the James Webb Space Telescope promises a new era of high-redshift
metallicity studies of previously unexplored regimes \citep[e.g.,][]{Sanders+2022}. We hope that this form will facilitate the flexibility needed to keep up with observations. 
% we hope that this form will facilitate a more sensible way for useful inference on large (future) datasets of astrophysical transients, such as the ever growing catalogue of gravitational wave transients. Our hope is that the constraints on the free parameters in the analytical form we propose, can provide a more useful guidance when comparing with the outcome of the predictions of cosmological simulations.

@@

We describe our model for \SFRDzZ in Section \ref{sec: model for sfrd(zZ)}.
We fit our model to to the star-forming gas in the Illustris TNG100 simulation in Section \ref{sec: fit against tng} we demonstrate an example application of our model by systematically varying the parameters that determine the shape of \SFRDzZ and investigate their impact on the local distribution of merging BBH masses in Section \ref{sec: mass dists}.
We summarise our findings in Section \ref{sec: summary}.

Throughout this work, we adopt a Kroupa initial mass function \citep{Kroupa2001} and a flat $\Lambda$CDM cosmology with $\Omega_{\rm{M}}=0.31$, $\Omega_{\rm{\Lambda}}=0.69$ and $H_0=67.7\rm{km\,s^{-1}\,Mpc^{-1}}$ \citep{Planck18_VI}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A convenient analytic expression for the metallicity-dependent star formation rate density \label{sec: model for sfrd(zZ)} }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We assume that the metallicity dependent star formation rate density can be separated into two independent functions \citep[e.g.\ ][]{Langer2006},

\begin{equation}
\label{eq: total sfrd}
\boxed{
        \SFRDzZ = \SFRDz \times \dPdZ.
        }
\end{equation}
The first term is the star formation rate density, \SFRDz, that is the amount of mass formed in stars per unit time and per unit comoving volume at each redshift, $z$. The second term, \dpdZ, is a probability density function that expresses what fraction of star formation occurs at which metallicity, $Z$, at each redshift.

@@

% $a=0.02$, $b=1.48$, $c=4.45$ and $d=5.9$ as best fitting parameters,
\subsection{The metallicity probability density function}
For the probability distribution of metallicities we draw inspiration from the approach by e.g., \cite{Neijssel+2019} who used a log-normal distribution. Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity. To capture this behaviour we adopt a skewed-log-normal distribution instead. This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep[first introduced by][]{Ohagan+1976}.

@@

\noindent where (a) is the standard log-normal distribution, $\phi$,
%
\begin{equation}
\label{eq: log normal and CDF}
 \phi \left(\frac{\ln Z - \xi}{\omega}\right) \equiv 
% \underbrace{
    \frac{1}{\sqrt{2 \pi}} 
    \exp{
         \left\{
            -\frac{1}{2} \left(\frac{\ln Z - \xi}{\omega}\right)^2
        \right\}
        }
  %  }_{(1)} 
    \end{equation}
and (b) is the new term that allows for asymmetry, which is equal to the cumulative of the log-normal distribution, $\Phi$,
    \begin{equation}
    \begin{array}{cc}
 \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right) &\equiv 
    \frac{1}{2} 
    \left[ 
        1 + {\rm erf}
            \left\{
                \alpha \frac{\ln Z - \xi}{\omega \sqrt{2}}
            \right\} 
    \right] \\
    \end{array}
\end{equation}

@@

\paragraph{The location and the mean of the metallicity distribution}
To obtain a useful expression for the redshift dependence of the ``location'' $\xi(z)$ we first express the expectation value or mean metallicity at a given redshift
% eq. 8 here: https://www-sciencedirect-com.ezp-prod1.hul.harvard.edu/science/article/pii/S0021850219300400
% Using k = 1 for the first moment
\begin{equation}
 \langle  Z \rangle 
 = 2 \exp
        \left(\xi +  \frac{\omega^2}{2} \right)
         \Phi\left(\beta\, \omega\right)
 \label{eqn:Zmean}
\end{equation}
where $\beta$ is 
\begin{equation}
\label{eq: beta}
\beta = \frac{\alpha}{\sqrt{1 + \alpha^2} }.
\end{equation}

For a more extended derivation of the moments of the skewed-log-normal, see e.g., \cite{WANG201995}.

\noindent For the evolution of the mean metallicity with redshift we follow \cite{Langer2006} and \cite{Neijssel+2019} in assuming that the mean of the probability density function of metallicities evolves with redshift as:
\begin{equation}
\label{eq: mean Z}
    \langle Z \rangle \equiv \mu(z) = \mu_0 \cdot 10^{\mu_z \cdot z},
\end{equation}
where $\mu_0
%= 0.025 
$ is the mean metallicity at redshift 0, and $\mu_z
%= -0.048
$ determines redshift evolution of the location. Equating this to Equation~\ref{eqn:Zmean}, we get an expression for $\xi(z)$,

@@

Note that the width, $w(z)$ is not the same as the variance. The variance, $\sigma(z)^2$, can be expressed as

\begin{equation}
    \sigma(z)^2 = \omega(z)^2 \left( 1 - \frac{2\beta^2}{\pi} \right)
\end{equation}

@@

\subsection{The overall cosmic star formation rate density}
For the star formation rate density, we assume the analytical form proposed by \cite{MadauDickinson2014},
\begin{eqnarray}
\label{eq: sfr1}
\boxed{
    \SFRDz  = 
    \frac{d^2 M_{\rm SFR}}{dt dV_c} (z)= 
    a \frac{\left(1 + z\right)^b}{1 + \left[ (1 + z)/c \right]^d} 
    }\,
\end{eqnarray}
in units of $\left[ \Msun \,yr^{-1} \,cMpc^{-3} \right]$. This introduces four parameters; $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic star formation rate density with redshift. \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{FitComparison_3panelPlot.py}
\includegraphics[width=0.9\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations.
The top panel shows the full two dimensional \SFRDzZ linear in time. The bottom left (right) panel shows slices of the distribution in redshift (metallicity). Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$. We show the TNG100 simulation data with thick gray lines. 
For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in each panel with grey dotted lines. For the latter, the contours in the top panel range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$. This shows that our analytical model adequately captures the \SFRDzZ of the TNG100 simulations.
 \label{fig: fit SFRD}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the Illustris-TNG cosmological simulations. 
We simultaneously fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star formation rate.

Below we briefly discuss the Illustris-TNG simulations, and elaborate on our fitting procedure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Illustris-TNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Both the large observational uncertainties in \SFRDzZ (as discussed in section \ref{sec: intro}), and the many uncertainties in cosmological simulations (as discussed below) call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work. 
% In particular, the advent of observations with the James Webb Space Telescope promises a new era of high-redshift% metallicity studies in previously unexplored regimes \citep[e.g.,][]{Sanders+2022}.
%
Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity dependent star formation rate density\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.

>>>>

% Title
% \title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation history  }
% \title{ A flexible expression for the metallicity-dependent cosmic star formation history: }
\title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation history.}

@@

%%%%%%%%%%%%%%%
\author[0000-0001-5484-4987]{L.~A.~C.~van~Son}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
60 Garden St., Cambridge, MA 02138, USA}
\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0001-9336-2825]{S. E. de Mink}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
\affiliation{Anton Pannekoek Institute of Astronomy, Science Park 904, University of Amsterdam, 1098XH Amsterdam, The Netherlands}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%%
\author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%%
\author[0000-0002-8901-6994]{L. Hernquist}
\affiliation{Center for Astrophysics $|$ Harvard $\&$ Smithsonian,
60 Garden St., Cambridge, MA 02138, USA}
%%%%%%%%%%%%%%%
\author[0000-0003-3308-2420]{R. Pakmor}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract with filler text
\begin{abstract}
New observational facilities are probing astrophysical transients such as stellar explosions and gravitational wave (GW) sources at ever increasing redshifts. To interpret these observations we need to compare them to predictions from stellar population models. Such models require the metallicity-dependent cosmic star formation history (\SFRDzZ) as an input. Large uncertainties remain in the shape and evolution of this function, and understanding its behaviour is essential to explain simulation results. 
% Large uncertainties remain in the value and shape of the \SFRDzZ, especially at the low metallicities that are crucial to the formation of GW events.
% Understanding the behaviour of the adopted metallicity distribution with which stars form is essential to explain simulation results. 
% Various approaches to approximate \SFRDzZ exist, ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
In this work, we propose a simple analytical function for \SFRDzZ. 
% The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
Variations of this function can be easily interpreted, because the parameters link to its shape in an intuitive way. %Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
We fit our analytical function to the star-forming gas of the cosmological TNG100 simulation and find that it is able to capture the main behaviour well. 
%
As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH). Our main findings are: I) the location of features is remarkably robust against variations in the metallicity-dependent cosmic star formation history, and II) the low mass end is least affected by these variations. This is promising as it increases our chances to constrain the physics that governs the formation of these objects.
% We further find that: III) the skewness, mean, and width of the metallicity distribution at low redshift affect the overall rate, while IV) the redshift evolution of the width and the mean of the metallicity distribution affects the slope at the high-mass end of the distribution. 
% IV) the shape of the overall star-formation rate density has a small impact on the local mass distribution.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction \label{sec: intro}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe. Exotic transient phenomena, including (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events appear to be especially sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe \citep[e.g.,][]{Langer+2007,Fruchter+2006,LIGO2016_implications}.
Gravitational astronomy in particular has seen explosive growth in the number of detections in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}, while theoretical predictions vary greatly due to uncertainties in the aforementioned metallicity of star formation \citep[e.g.,][]{Santoliquido+2021,Broekgaarden+2021b}. In order to correctly model and interpret these observations, it is thus fundamental to know the rate of star formation at different metallicities throughout cosmic history; i.e. the metallicity-dependent cosmic star formation history \citep[\SFRDzZ, see also the recent review by][]{chruslinska2022_review}. Throughout this work little $z$ refers to the redshift and $Z$ to the metallicity of star formation.

It is difficult to observationally constrain the shape of \SFRDzZ\ -- \citep[see e.g., ][for discussion of relevant observational caveats]{Chruslinska2019_obs,Boco+2021}. Even at low redshifts, the low metallicity part of the distribution is poorly constrained \citep{Chruslinska+2021}.
Nonetheless, several methods exist to estimate the metallicity-dependent cosmic star formation history.

% combines a  with an approximation of the metallicity distribution that
The first method is based on empirical scaling relations, linking galaxy properties like stellar mass $M_{\star}$, metallicity $Z$, and overall star-formation rate density \SFRDz, with the GSMF galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}. However, the applied methods to infer galaxy properties and subsequently scaling relations such as the MZ-relation differ greatly, which makes it difficult to interpret these results in a consistent way \citep[e.g.,][]{KewleyEllison2008,MaiolinoMannucci2019,Cresci+2019}. Moreover, observations are generally incomplete at high redshifts and low galaxy luminosity \citep[e.g.,][]{Chruslinska+2021}.

% \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
One can also directly extract the metallicity-dependent cosmic star formation history from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2022_rates}. However, these simulations currently lack the resolution to resolve the lowest mass galaxies, and their variations in \SFRDzZ span a smaller range than those observed in observationally-based models \citep{Pakmor+2022}.

Alternatively, one can combine analytical models for the observed overall star-formation rate density, \SFRDz, like those from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with an assumed function for the shape of the cosmic metallicity density distribution, such as was was done in e.g., \cite{LangerNorman2006} and the phenomenological model in \cite{Neijssel+2019}.

%Arguments: cosmological simulations work at high z,  but are they real? observations 
In this work we follow the latter approach and propose a flexible analytical model for \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available. 
In contrast to earlier work, we adopt a skewed-lognormal distribution of metallicities that can capture the asymmetry in the low and high metallicity tails.

The purpose of this proposed form is twofold.  
First of all, the form we propose allows for an intuitive interpretation of the free parameters. This allows us to get better insight of the impact of changes in these parameters on the inferred ranges of astrophysical transients (as we demonstrate in Section \ref{sec: mass dists} using GW predictions as an example). By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties can be systematically explored.
%
Secondly, both the large complications in observational constraints, and the many uncertainties in cosmological simulations call for a generalised form of \SFRDzZ that can be easily updated when new information becomes available. % which is the motivation for this work. 
In particular, the advent of observations with the James Webb Space Telescope promises a new era of high-redshift
metallicity studies of previously unexplored regimes \citep[e.g.,][]{Sanders+2022}. We hope that this form will facilitate the flexibility needed to keep up with observations. 
% we hope that this form will facilitate a more sensible way for useful inference on large (future) datasets of astrophysical transients, such as the ever growing catalogue of gravitational wave transients. Our hope is that the constraints on the free parameters in the analytical form we propose, can provide a more useful guidance when comparing with the outcome of the predictions of cosmological simulations.

@@

We describe our model for \SFRDzZ in Section \ref{sec: model for sfrd(zZ)}.
We fit our model to the star-forming gas in the Illustris TNG100 simulation in Section \ref{sec: fit against tng}, and demonstrate an example application of our model by systematically varying the parameters that determine the shape of \SFRDzZ and investigate their impact on the local distribution of merging BBH masses in Section \ref{sec: mass dists}.
We summarise our findings in Section \ref{sec: summary}.

Throughout this work, we adopt a universal Kroupa initial mass function \citep{Kroupa2001} with the mass
limits $0.01–200\Msun$ and a flat $\Lambda$CDM cosmology with $\Omega_{\rm{M}}=0.31$, $\Omega_{\rm{\Lambda}}=0.69$ and $H_0=67.7\rm{km\,s^{-1}\,Mpc^{-1}}$ \citep{Planck18_VI}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A convenient analytic expression for the metallicity-dependent cosmic star formation history \label{sec: model for sfrd(zZ)} }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We assume that the metallicity-dependent cosmic star formation history can be separated into two independent functions 
(as was assumed in e.g., \citealt{LangerNorman2006}, but cf. \citealt{chruslinska2022_review} for a discussion on the validity on this assumption).

\begin{equation}
\label{eq: total sfrd}
\boxed{
        \SFRDzZ = \SFRDz \times \dPdZ.
        }
\end{equation}
The first term is the star formation rate density, \SFRDz, that is the amount of mass formed in stars per unit time and per unit comoving volume at each redshift, $z$. The second term, \dpdZ, is a probability density distribution that expresses what fraction of star formation occurs at which metallicity, $Z$, at each redshift.

@@

% $a=0.02$, $b=1.48$, $c=4.45$ and $d=5.9$ as best fitting parameters,
\subsection{The cosmic metallicity density distribution}
For the probability distribution of metallicities we draw inspiration from the approach by e.g., \cite{Neijssel+2019} who used a log-normal distribution for their phenomenological model. Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity. To capture this behaviour we adopt a skewed-log-normal distribution instead. This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep[first introduced by][]{Ohagan+1976}.

@@

\noindent where (a) is the standard log-normal distribution, $\phi$,
%
\begin{equation}
\label{eq: log normal and CDF}
 \phi \left(\frac{\ln Z - \xi}{\omega}\right) \equiv 
% \underbrace{
    \frac{1}{\sqrt{2 \pi}} 
    \exp{
         \left\{
            -\frac{1}{2} \left(\frac{\ln Z - \xi}{\omega}\right)^2
        \right\}
        }
  %  }_{(1)} 
    \end{equation}
and (b) is the new term that allows for asymmetry, which is equal to the cumulative of the log-normal distribution, $\Phi$,
    \begin{equation}
    \begin{array}{cc}
 \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right) &\equiv 
    \frac{1}{2} 
    \left[ 
        1 + {\rm erf}
            \left\{
                \alpha \frac{\ln Z - \xi}{\omega \sqrt{2}}
            \right\} 
    \right] . \\
    \end{array}
\end{equation}

@@

\paragraph{The location and the mean of the metallicity distribution}
To obtain a useful expression for the redshift dependence of the ``location'' $\xi(z)$ we first express the expectation value or mean metallicity at a given redshift
% eq. 8 here: https://www-sciencedirect-com.ezp-prod1.hul.harvard.edu/science/article/pii/S0021850219300400
% Using k = 1 for the first moment
\begin{equation}
 \langle  Z \rangle 
 = 2 \exp
        \left(\xi +  \frac{\omega^2}{2} \right)
         \Phi\left(\beta\, \omega\right)
 \label{eqn:Zmean}
\end{equation}
where $\beta$ is 
\begin{equation}
\label{eq: beta}
\beta = \frac{\alpha}{\sqrt{1 + \alpha^2} }.
\end{equation}
(For a more extended derivation of the moments of the skewed-log-normal, see e.g., \cite{WANG201995}.)

For the evolution of the mean metallicity with redshift we follow \cite{LangerNorman2006} and the phenomenological model from \cite{Neijssel+2019} in assuming that the mean of the probability density function of metallicities evolves with redshift as:
\begin{equation}
\label{eq: mean Z}
    \langle Z \rangle \equiv \mu(z) = \mu_0 \cdot 10^{\mu_z \cdot z},
\end{equation}
where $\mu_0
%= 0.025 
$ is the mean metallicity at redshift 0, and $\mu_z
%= -0.048
$ determines redshift evolution of the location. Equating this to Equation~\ref{eqn:Zmean}, we get an expression for $\xi(z)$,

@@

Note that the width, $w(z)$ is not the same as the variance. The variance, $\sigma^2(z)$, can be expressed as

\begin{equation}
    \sigma^2(z) = \omega^2(z) \left( 1 - \frac{2\beta^2}{\pi} \right)
\end{equation}

@@

\subsection{The overall cosmic star formation rate density}
For the star formation rate density, we assume the analytical form proposed by \cite{MadauDickinson2014},
\begin{eqnarray}
\label{eq: sfr1}
\boxed{
    \SFRDz  = 
    \frac{d^2 M_{\rm SFR}}{dt dV_c} (z)= 
    a \frac{\left(1 + z\right)^b}{1 + \left[ (1 + z)/c \right]^d} 
    }\,
\end{eqnarray}
in units of $\left[ \Msun \,yr^{-1} \,cMpc^{-3} \right]$. This introduces four parameters: $a$ which sets the overal normalisation and which has the same units as \SFRDz and $b,c$ and $d$ which are unitless and which govern the shape of the overal cosmic star formation rate density with redshift. \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{FitComparison_3panelPlot.py}
\includegraphics[width=0.9\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations. The top panel shows the full two dimensional \SFRDzZ linear in time. Contours range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$. 
The bottom left (right) panel shows slices of the distribution in redshift (metallicity). Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$ (note the linear scale of \SFRDzZ in the bottom channel). We show the TNG100 simulation data with thick gray lines. 
For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in all panels with grey dotted lines. The bottom panels show that our analytical model adequately captures the shape of the \SFRDzZ from TNG100.
 \label{fig: fit SFRD}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the IllustrisTNG cosmological simulations. 
We simultaneously fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star-formation rate density.
Below we briefly discuss the IllustrisTNG simulations, and elaborate on our fitting procedure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{IllustrisTNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Both the large observational uncertainties in \SFRDzZ (as discussed in section \ref{sec: intro}), and the many uncertainties in cosmological simulations (as discussed below) call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work. 
% In particular, the advent of observations with the James Webb Space Telescope promises a new era of high-redshift% metallicity studies in previously unexplored regimes \citep[e.g.,][]{Sanders+2022}.
%
Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity-dependent cosmic star formation history\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.

The IllustrisTNG-project (or TNG in short) considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations \citep[][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018, Nelson2019a, Pillepich2019}.
Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations. In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.
% Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.
